X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-10 hedpc.tex
abbreviated journals

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{babel}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bf,small,labelsep=period]{caption}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}
\usepackage[affil-it]{authblk}

@@

@@

\author[1,2]{T.~Thüring}
\author[1,2]{M.~Abis}
\author[1]{Z.~Wang}
\author[1]{C.~David}
\author[1,2]{M.~Stampanoni}
\affil[1]{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affil[2]{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}

@@

X-ray radiography and \ac{CT} are standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
diagnostic tasks in medicine. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering~\cite{Als-Nielsen2011}.

@@

Phase-sensitive imaging is a desirable modality, since it delivers a
complementary source of contrast with respect to absorption by providing
direct access to the electron density~\cite{Als-Nielsen2011}. Moreover, the
combination with attenuation enables the determination of the effective
atomic number~\cite{Qi2010}. An enhanced \ac{CNR} compared to
attenuation for certain materials or
tissues~\cite{Pfeiffer2007a,McDonald2009} has also been demonstrated.

@@

\bibitem{Als-Nielsen2011}
\bibinfo{author}{Als-Nielsen, J.} \& \bibinfo{author}{McMorrow, D.}
\newblock \emph{\bibinfo{title}{{Elements of modern X-ray physics}}}
  (\bibinfo{year}{2011}).

\bibitem{Qi2010}
\bibinfo{author}{Qi, Z.}, \bibinfo{author}{Zambelli, J.},
  \bibinfo{author}{Bevins, N.} \& \bibinfo{author}{Chen, G.-H.}
\newblock \bibinfo{title}{{Quantitative imaging of electron density and
  effective atomic number using phase contrast CT.}}
\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
  \textbf{\bibinfo{volume}{55}}, \bibinfo{pages}{2669--77}
  (\bibinfo{year}{2010}).

\bibitem{Pfeiffer2007a}
\bibinfo{author}{Pfeiffer, F.} \emph{et~al.}
\newblock \bibinfo{title}{{High-resolution brain tumor visualization using
  three-dimensional x-ray phase contrast tomography.}}
\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
  \textbf{\bibinfo{volume}{52}}, \bibinfo{pages}{6923--6930}
  (\bibinfo{year}{2007}).

\bibitem{McDonald2009}
\bibinfo{author}{McDonald, S.~A.} \emph{et~al.}
\newblock \bibinfo{title}{{Advanced phase-contrast imaging using a grating
  interferometer}}.
\newblock \emph{\bibinfo{journal}{Journal of Synchrotron Radiation}}
  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{562--572}
  (\bibinfo{year}{2009}).

\bibitem{Davis1995}
\bibinfo{author}{Davis, T.}, \bibinfo{author}{Gao, D.},
  \bibinfo{author}{Gureyev, T.}, \bibinfo{author}{Stevenson, A.} \&
  \bibinfo{author}{Wilkins, S.}
\newblock \bibinfo{title}{{Phase-contrast imaging of weakly absorbing materials
  using hard X-rays}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{373}},
  \bibinfo{pages}{595--598} (\bibinfo{year}{1995}).

\bibitem{Chapman1997}
\bibinfo{author}{Chapman, D.} \emph{et~al.}
\newblock \bibinfo{title}{{Diffraction enhanced x-ray imaging}}.
\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{2015--2025}
  (\bibinfo{year}{1997}).

\bibitem{Bonse1965}
\bibinfo{author}{Bonse, U.} \& \bibinfo{author}{Hart, M.}
\newblock \bibinfo{title}{{An x-ray interferometer}}.
\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{155--156}
  (\bibinfo{year}{1965}).

\bibitem{Momose1996}
\bibinfo{author}{Momose, A.}, \bibinfo{author}{Takeda, T.},
  \bibinfo{author}{Itai, Y.} \& \bibinfo{author}{Hirano, K.}
\newblock \bibinfo{title}{{Phase-contrast X-ray computed tomography for
  observing biological soft tissues}}.
\newblock \emph{\bibinfo{journal}{Nature Medicine}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{473--475}
  (\bibinfo{year}{1996}).

\bibitem{Snigirev1995}
\bibinfo{author}{Snigirev, A.}, \bibinfo{author}{Snigireva, I.},
  \bibinfo{author}{Kohn, V.}, \bibinfo{author}{Kuznetsov, S.} \&
  \bibinfo{author}{Schelokov, I.}
\newblock \bibinfo{title}{{On the possibilities of x-ray phase contrast
  microimaging by coherent high-energy synchrotron radiation}}.
\newblock \emph{\bibinfo{journal}{Review of Scientific Instruments}}
  \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{5486--5492}
  (\bibinfo{year}{1995}).

\bibitem{Wilkins1996}
\bibinfo{author}{Wilkins, S.}, \bibinfo{author}{Gureyev, T.},
  \bibinfo{author}{Gao, D.}, \bibinfo{author}{Pogany, A.} \&
  \bibinfo{author}{Stevenson, A.}
\newblock \bibinfo{title}{{Phase-contrast imaging using polychromatic hard
  X-rays}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{384}},
  \bibinfo{pages}{335--338} (\bibinfo{year}{1996}).

\bibitem{Cloetens1996}
\bibinfo{author}{Cloetens, P.}, \bibinfo{author}{Barrett, R.},
  \bibinfo{author}{Baruchel, J.}, \bibinfo{author}{Guigay, J.} \&
  \bibinfo{author}{Schlenker, M.}
\newblock \bibinfo{title}{{Phase objects in synchrotron radiation hard x-ray
  imaging}}.
\newblock \emph{\bibinfo{journal}{Journal of Physics D: Applied Physics}}
  \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{133--146}
  (\bibinfo{year}{1996}).

\bibitem{Cloetens1997}
\bibinfo{author}{Cloetens, P.}, \bibinfo{author}{Guigay, J.},
  \bibinfo{author}{{De Martino}, C.}, \bibinfo{author}{Baruchel, J.} \&
  \bibinfo{author}{Schlenker, M.}
\newblock \bibinfo{title}{{Fractional Talbot imaging of phase gratings with
  hard x rays.}}
\newblock \emph{\bibinfo{journal}{Optics Letters}}
  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{1059--61}
  (\bibinfo{year}{1997}).

\bibitem{David2002}
\bibinfo{author}{David, C.}, \bibinfo{author}{N\"{o}hammer, B.},
  \bibinfo{author}{Solak, H.} \& \bibinfo{author}{Ziegler, E.}
\newblock \bibinfo{title}{{Differential x-ray phase contrast imaging using a
  shearing interferometer}}.
\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
  \textbf{\bibinfo{volume}{81}}, \bibinfo{pages}{3287--3289}
  (\bibinfo{year}{2002}).

\bibitem{Momose2003a}
\bibinfo{author}{Momose, A.} \emph{et~al.}
\newblock \bibinfo{title}{{Demonstration of X-Ray Talbot Interferometry}}.
\newblock \emph{\bibinfo{journal}{Japanese Journal of Applied Physics}}
  \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{L866--L868}
  (\bibinfo{year}{2003}).

\bibitem{Munro2012}
\bibinfo{author}{Munro, P.}, \bibinfo{author}{Ignatyev, K.},
  \bibinfo{author}{Speller, R.} \& \bibinfo{author}{Olivo, A.}
\newblock \bibinfo{title}{{Phase and absorption retrieval using incoherent
  X-ray sources}}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{2012}}, \bibinfo{pages}{2--7}
  (\bibinfo{year}{2012}).

\bibitem{Pfeiffer2006}
\bibinfo{author}{Pfeiffer, F.}, \bibinfo{author}{Weitkamp, T.},
  \bibinfo{author}{Bunk, O.} \& \bibinfo{author}{David, C.}
\newblock \bibinfo{title}{{Phase retrieval and differential phase-contrast
  imaging with low-brilliance X-ray sources}}.
\newblock \emph{\bibinfo{journal}{Nature Physics}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{258--261}
  (\bibinfo{year}{2006}).

\bibitem{Nesch2009}
\bibinfo{author}{Nesch, I.} \emph{et~al.}
\newblock \bibinfo{title}{{The design and application of an in-laboratory
  diffraction-enhanced x-ray imaging instrument.}}
\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
  \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{093702}
  (\bibinfo{year}{2009}).

\bibitem{Parham2009}
\bibinfo{author}{Parham, C.}, \bibinfo{author}{Zhong, Z.},
  \bibinfo{author}{Connor, D.~M.}, \bibinfo{author}{Chapman, L.~D.} \&
  \bibinfo{author}{Pisano, E.~D.}
\newblock \bibinfo{title}{Design and implementation of a compact low-dose
  diffraction enhanced medical imaging system}.
\newblock \emph{\bibinfo{journal}{Academic Radiology}}
  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{911 -- 917}
  (\bibinfo{year}{2009}).

\bibitem{Pfeiffer2008}
\bibinfo{author}{Pfeiffer, F.} \emph{et~al.}
\newblock \bibinfo{title}{{Hard-X-ray dark-field imaging using a grating
  interferometer}}.
\newblock \emph{\bibinfo{journal}{Nature Materials}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{134--137}
  (\bibinfo{year}{2008}).

\bibitem{Willner2013}
\bibinfo{author}{Willner, M.} \emph{et~al.}
\newblock \bibinfo{title}{{Quantitative X-ray phase-contrast computed
  tomography at 82 keV}}.
\newblock \emph{\bibinfo{journal}{Optics Express}}
  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{4155--4166}
  (\bibinfo{year}{2013}).

\bibitem{Donath2009a}
\bibinfo{author}{Donath, T.} \emph{et~al.}
\newblock \bibinfo{title}{{Phase-contrast imaging and tomography at 60 keV
  using a conventional x-ray tube source.}}
\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
  \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{053701}
  (\bibinfo{year}{2009}).

\bibitem{Mohr2012}
\bibinfo{author}{Mohr, J.} \emph{et~al.}
\newblock \bibinfo{title}{High aspect ratio gratings for x-ray phase contrast
  imaging}.
\newblock \emph{\bibinfo{journal}{AIP Conference Proceedings}}
  \textbf{\bibinfo{volume}{1466}}, \bibinfo{pages}{41--50}
  (\bibinfo{year}{2012}).

\bibitem{David2007}
\bibinfo{author}{David, C.} \emph{et~al.}
\newblock \bibinfo{title}{{Fabrication of diffraction gratings for hard X-ray
  phase contrast imaging}}.
\newblock \emph{\bibinfo{journal}{Microelectronic Engineering}}
  \textbf{\bibinfo{volume}{84}}, \bibinfo{pages}{1172--1177}
  (\bibinfo{year}{2007}).

@@

\bibitem{Stutman2012a}
\bibinfo{author}{Stutman, D.} \& \bibinfo{author}{Finkenthal, M.}
\newblock \bibinfo{title}{{Glancing angle Talbot-Lau grating interferometers
  for phase contrast imaging at high x-ray energy}}.
\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
  \textbf{\bibinfo{volume}{101}}, \bibinfo{pages}{91108}
  (\bibinfo{year}{2012}).

@@

\bibitem{Weitkamp2005}
\bibinfo{author}{Weitkamp, T.} \emph{et~al.}
\newblock \bibinfo{title}{{X-ray phase imaging with a grating interferometer}}.
\newblock \emph{\bibinfo{journal}{Optics Express}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{6296--6304}
  (\bibinfo{year}{2005}).

\bibitem{Thuering2013c}
\bibinfo{author}{Thuering, T.} \emph{et~al.}
\newblock \bibinfo{title}{{Energy resolved X-ray grating interferometry}}.
\newblock \emph{\bibinfo{journal}{Applied Physics Letters}}
  \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{191113}
  (\bibinfo{year}{2013}).

\bibitem{Chabior2011a}
\bibinfo{author}{Chabior, M.} \emph{et~al.}
\newblock \bibinfo{title}{{Beam hardening effects in grating-based x-ray
  phase-contrast imaging}}.
\newblock \emph{\bibinfo{journal}{Medical Physics}}
  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{1189} (\bibinfo{year}{2011}).

\bibitem{Momose2005}
\bibinfo{author}{Momose, A.}
\newblock \bibinfo{title}{{Recent Advances in X-ray Phase Imaging}}.
\newblock \emph{\bibinfo{journal}{Japanese Journal of Applied Physics}}
  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{6355--6367}
  (\bibinfo{year}{2005}).

\bibitem{Grunzweig2008}
\bibinfo{author}{Gr\"{u}nzweig, C.} \emph{et~al.}
\newblock \bibinfo{title}{{Design, fabrication, and characterization of
  diffraction gratings for neutron phase contrast imaging.}}
\newblock \emph{\bibinfo{journal}{The Review of Scientific Instruments}}
  \textbf{\bibinfo{volume}{79}}, \bibinfo{pages}{053703}
  (\bibinfo{year}{2008}).

\bibitem{Raupach2011}
\bibinfo{author}{Raupach, R.} \& \bibinfo{author}{Flohr, T.~G.}
\newblock \bibinfo{title}{{Analytical evaluation of the signal and noise
  propagation in x-ray differential phase-contrast computed tomography.}}
\newblock \emph{\bibinfo{journal}{Physics in Medicine and Biology}}
  \textbf{\bibinfo{volume}{56}}, \bibinfo{pages}{2219--2244}
  (\bibinfo{year}{2011}).

>>>>

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{babel}
\usepackage{jabbrv}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bf,small,labelsep=period]{caption}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}
\usepackage[affil-it]{authblk}

@@

\DefineJournalPartialAbbreviation{Medicine}{Med}
\DefineJournalPartialAbbreviation{Instrumentation}{Instr}
\DefineJournalPartialAbbreviation{Instruments}{Instr}
\DefineJournalPartialAbbreviation{Express}{Expr}
\DefineJournalPartialAbbreviation{Synchrotron}{Synch}

@@

\author[1,2]{T.~Thüring}
\author[1,2]{M.~Abis\thanks{\texttt{matteo.abis@psi.ch}; Corresponding author.}}
\author[1]{Z.~Wang}
\author[1]{C.~David}
\author[1,2]{M.~Stampanoni}
\affil[1]{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affil[2]{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}

@@

X-ray radiography and \ac{CT} are standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
diagnostic tasks in medicine. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering~\cite[extras={, p.~280}]{Als-Nielsen2011}.

@@

Phase-sensitive imaging is a desirable modality, since it delivers a
complementary source of contrast with respect to absorption by providing
direct access to the electron density~\cite[extras{, p.71}]{Als-Nielsen2011}. Moreover, the
combination with attenuation enables the determination of the effective
atomic number~\cite{Qi2010}. An enhanced \ac{CNR} compared to
attenuation for certain materials or
tissues~\cite{Pfeiffer2007a,McDonald2009} has also been demonstrated.

@@

\bibitem{Als-Nielsen2011}
\bibinfo{author}{Als-Nielsen, J.} \& \bibinfo{author}{McMorrow, D.}
\newblock \emph{\bibinfo{title}{{Elements of modern X-ray physics}}}
  (\bibinfo{publisher}{Wiley}, \bibinfo{address}{London},
  \bibinfo{year}{2011}), \bibinfo{edition}{2nd} edn.

\bibitem{Qi2010}
\bibinfo{author}{Qi, Z.}, \bibinfo{author}{Zambelli, J.},
  \bibinfo{author}{Bevins, N.} \& \bibinfo{author}{Chen, G.-H.}
\newblock \bibinfo{title}{{Quantitative imaging of electron density and
  effective atomic number using phase contrast CT.}}
\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
  Biology}}} \textbf{\bibinfo{volume}{55}}, \bibinfo{pages}{2669--77}
  (\bibinfo{year}{2010}).

\bibitem{Pfeiffer2007a}
\bibinfo{author}{Pfeiffer, F.} \emph{et~al.}
\newblock \bibinfo{title}{{High-resolution brain tumor visualization using
  three-dimensional x-ray phase contrast tomography.}}
\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
  Biology}}} \textbf{\bibinfo{volume}{52}}, \bibinfo{pages}{6923--6930}
  (\bibinfo{year}{2007}).

\bibitem{McDonald2009}
\bibinfo{author}{McDonald, S.~A.} \emph{et~al.}
\newblock \bibinfo{title}{{Advanced phase-contrast imaging using a grating
  interferometer}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Journal of Synchrotron
  Radiation}}} \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{562--572}
  (\bibinfo{year}{2009}).

\bibitem{Davis1995}
\bibinfo{author}{Davis, T.}, \bibinfo{author}{Gao, D.},
  \bibinfo{author}{Gureyev, T.}, \bibinfo{author}{Stevenson, A.} \&
  \bibinfo{author}{Wilkins, S.}
\newblock \bibinfo{title}{{Phase-contrast imaging of weakly absorbing materials
  using hard X-rays}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature}}}
  \textbf{\bibinfo{volume}{373}}, \bibinfo{pages}{595--598}
  (\bibinfo{year}{1995}).

\bibitem{Chapman1997}
\bibinfo{author}{Chapman, D.} \emph{et~al.}
\newblock \bibinfo{title}{{Diffraction enhanced x-ray imaging}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
  Biology}}} \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{2015--2025}
  (\bibinfo{year}{1997}).

\bibitem{Bonse1965}
\bibinfo{author}{Bonse, U.} \& \bibinfo{author}{Hart, M.}
\newblock \bibinfo{title}{{An x-ray interferometer}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Applied Physics Letters}}}
  \textbf{\bibinfo{volume}{6}}, \bibinfo{pages}{155--156}
  (\bibinfo{year}{1965}).

\bibitem{Momose1996}
\bibinfo{author}{Momose, A.}, \bibinfo{author}{Takeda, T.},
  \bibinfo{author}{Itai, Y.} \& \bibinfo{author}{Hirano, K.}
\newblock \bibinfo{title}{{Phase-contrast X-ray computed tomography for
  observing biological soft tissues}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature Medicine}}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{473--475}
  (\bibinfo{year}{1996}).

\bibitem{Snigirev1995}
\bibinfo{author}{Snigirev, A.}, \bibinfo{author}{Snigireva, I.},
  \bibinfo{author}{Kohn, V.}, \bibinfo{author}{Kuznetsov, S.} \&
  \bibinfo{author}{Schelokov, I.}
\newblock \bibinfo{title}{{On the possibilities of x-ray phase contrast
  microimaging by coherent high-energy synchrotron radiation}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Review of Scientific
  Instruments}}} \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{5486--5492}
  (\bibinfo{year}{1995}).

\bibitem{Wilkins1996}
\bibinfo{author}{Wilkins, S.}, \bibinfo{author}{Gureyev, T.},
  \bibinfo{author}{Gao, D.}, \bibinfo{author}{Pogany, A.} \&
  \bibinfo{author}{Stevenson, A.}
\newblock \bibinfo{title}{{Phase-contrast imaging using polychromatic hard
  X-rays}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature}}}
  \textbf{\bibinfo{volume}{384}}, \bibinfo{pages}{335--338}
  (\bibinfo{year}{1996}).

\bibitem{Cloetens1996}
\bibinfo{author}{Cloetens, P.}, \bibinfo{author}{Barrett, R.},
  \bibinfo{author}{Baruchel, J.}, \bibinfo{author}{Guigay, J.} \&
  \bibinfo{author}{Schlenker, M.}
\newblock \bibinfo{title}{{Phase objects in synchrotron radiation hard x-ray
  imaging}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Journal of Physics D: Applied
  Physics}}} \textbf{\bibinfo{volume}{29}}, \bibinfo{pages}{133--146}
  (\bibinfo{year}{1996}).

\bibitem{Cloetens1997}
\bibinfo{author}{Cloetens, P.}, \bibinfo{author}{Guigay, J.},
  \bibinfo{author}{{De Martino}, C.}, \bibinfo{author}{Baruchel, J.} \&
  \bibinfo{author}{Schlenker, M.}
\newblock \bibinfo{title}{{Fractional Talbot imaging of phase gratings with
  hard x rays.}}
\newblock \emph{\JournalTitle{\bibinfo{journal}{Optics Letters}}}
  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{1059--61}
  (\bibinfo{year}{1997}).

\bibitem{David2002}
\bibinfo{author}{David, C.}, \bibinfo{author}{N\"{o}hammer, B.},
  \bibinfo{author}{Solak, H.} \& \bibinfo{author}{Ziegler, E.}
\newblock \bibinfo{title}{{Differential x-ray phase contrast imaging using a
  shearing interferometer}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Appl. Phys. Lett.}}}
  \textbf{\bibinfo{volume}{81}}, \bibinfo{pages}{3287--3289}
  (\bibinfo{year}{2002}).

\bibitem{Momose2003a}
\bibinfo{author}{Momose, A.} \emph{et~al.}
\newblock \bibinfo{title}{{Demonstration of X-Ray Talbot Interferometry}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Japanese Journal of Applied
  Physics}}} \textbf{\bibinfo{volume}{42}}, \bibinfo{pages}{L866--L868}
  (\bibinfo{year}{2003}).

\bibitem{Munro2012}
\bibinfo{author}{Munro, P.}, \bibinfo{author}{Ignatyev, K.},
  \bibinfo{author}{Speller, R.} \& \bibinfo{author}{Olivo, A.}
\newblock \bibinfo{title}{{Phase and absorption retrieval using incoherent
  X-ray sources}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Proceedings of the National
  Academy of Sciences}}} \textbf{\bibinfo{volume}{2012}}, \bibinfo{pages}{2--7}
  (\bibinfo{year}{2012}).

\bibitem{Pfeiffer2006}
\bibinfo{author}{Pfeiffer, F.}, \bibinfo{author}{Weitkamp, T.},
  \bibinfo{author}{Bunk, O.} \& \bibinfo{author}{David, C.}
\newblock \bibinfo{title}{{Phase retrieval and differential phase-contrast
  imaging with low-brilliance X-ray sources}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature Physics}}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{258--261}
  (\bibinfo{year}{2006}).

\bibitem{Nesch2009}
\bibinfo{author}{Nesch, I.} \emph{et~al.}
\newblock \bibinfo{title}{{The design and application of an in-laboratory
  diffraction-enhanced x-ray imaging instrument.}}
\newblock \emph{\JournalTitle{\bibinfo{journal}{The Review of Scientific
  Instruments}}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{093702}
  (\bibinfo{year}{2009}).

\bibitem{Parham2009}
\bibinfo{author}{Parham, C.}, \bibinfo{author}{Zhong, Z.},
  \bibinfo{author}{Connor, D.~M.}, \bibinfo{author}{Chapman, L.~D.} \&
  \bibinfo{author}{Pisano, E.~D.}
\newblock \bibinfo{title}{Design and implementation of a compact low-dose
  diffraction enhanced medical imaging system}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Academic Radiology}}}
  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{911 -- 917}
  (\bibinfo{year}{2009}).

\bibitem{Pfeiffer2008}
\bibinfo{author}{Pfeiffer, F.} \emph{et~al.}
\newblock \bibinfo{title}{{Hard-X-ray dark-field imaging using a grating
  interferometer}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Nature Materials}}}
  \textbf{\bibinfo{volume}{7}}, \bibinfo{pages}{134--137}
  (\bibinfo{year}{2008}).

\bibitem{Willner2013}
\bibinfo{author}{Willner, M.} \emph{et~al.}
\newblock \bibinfo{title}{{Quantitative X-ray phase-contrast computed
  tomography at 82 keV}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Optics Express}}}
  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{4155--4166}
  (\bibinfo{year}{2013}).

\bibitem{Donath2009a}
\bibinfo{author}{Donath, T.} \emph{et~al.}
\newblock \bibinfo{title}{{Phase-contrast imaging and tomography at 60 keV
  using a conventional x-ray tube source.}}
\newblock \emph{\JournalTitle{\bibinfo{journal}{The Review of Scientific
  Instruments}}} \textbf{\bibinfo{volume}{80}}, \bibinfo{pages}{053701}
  (\bibinfo{year}{2009}).

\bibitem{Mohr2012}
\bibinfo{author}{Mohr, J.} \emph{et~al.}
\newblock \bibinfo{title}{High aspect ratio gratings for x-ray phase contrast
  imaging}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{AIP Conference Proceedings}}}
  \textbf{\bibinfo{volume}{1466}}, \bibinfo{pages}{41--50}
  (\bibinfo{year}{2012}).

\bibitem{David2007}
\bibinfo{author}{David, C.} \emph{et~al.}
\newblock \bibinfo{title}{{Fabrication of diffraction gratings for hard X-ray
  phase contrast imaging}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Microelectronic Engineering}}}
  \textbf{\bibinfo{volume}{84}}, \bibinfo{pages}{1172--1177}
  (\bibinfo{year}{2007}).

@@

\bibitem{Stutman2012a}
\bibinfo{author}{Stutman, D.} \& \bibinfo{author}{Finkenthal, M.}
\newblock \bibinfo{title}{{Glancing angle Talbot-Lau grating interferometers
  for phase contrast imaging at high x-ray energy}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Applied Physics Letters}}}
  \textbf{\bibinfo{volume}{101}}, \bibinfo{pages}{91108}
  (\bibinfo{year}{2012}).

@@

\bibitem{Weitkamp2005}
\bibinfo{author}{Weitkamp, T.} \emph{et~al.}
\newblock \bibinfo{title}{{X-ray phase imaging with a grating interferometer}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Optics Express}}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{6296--6304}
  (\bibinfo{year}{2005}).

\bibitem{Thuering2013c}
\bibinfo{author}{Thuering, T.} \emph{et~al.}
\newblock \bibinfo{title}{{Energy resolved X-ray grating interferometry}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Applied Physics Letters}}}
  \textbf{\bibinfo{volume}{102}}, \bibinfo{pages}{191113}
  (\bibinfo{year}{2013}).

\bibitem{Chabior2011a}
\bibinfo{author}{Chabior, M.} \emph{et~al.}
\newblock \bibinfo{title}{{Beam hardening effects in grating-based x-ray
  phase-contrast imaging}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Medical Physics}}}
  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{1189} (\bibinfo{year}{2011}).

\bibitem{Momose2005}
\bibinfo{author}{Momose, A.}
\newblock \bibinfo{title}{{Recent Advances in X-ray Phase Imaging}}.
\newblock \emph{\JournalTitle{\bibinfo{journal}{Japanese Journal of Applied
  Physics}}} \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{6355--6367}
  (\bibinfo{year}{2005}).

\bibitem{Grunzweig2008}
\bibinfo{author}{Gr\"{u}nzweig, C.} \emph{et~al.}
\newblock \bibinfo{title}{{Design, fabrication, and characterization of
  diffraction gratings for neutron phase contrast imaging.}}
\newblock \emph{\JournalTitle{\bibinfo{journal}{The Review of Scientific
  Instruments}}} \textbf{\bibinfo{volume}{79}}, \bibinfo{pages}{053703}
  (\bibinfo{year}{2008}).

\bibitem{Raupach2011}
\bibinfo{author}{Raupach, R.} \& \bibinfo{author}{Flohr, T.~G.}
\newblock \bibinfo{title}{{Analytical evaluation of the signal and noise
  propagation in x-ray differential phase-contrast computed tomography.}}
\newblock \emph{\JournalTitle{\bibinfo{journal}{Physics in Medicine and
  Biology}}} \textbf{\bibinfo{volume}{56}}, \bibinfo{pages}{2219--2244}
  (\bibinfo{year}{2011}).
